Gsmodutils: A python based framework for test driven genome scale metabolic model development

### 2018-08-30 article/article.tex
EPS figures

\title{Gsmodutils: A python based framework for test driven genome scale metabolic model development}
\author[1,2]{James P Gilbert}
\author[1,2]{Nicole Pearcy}
\author[1]{Rupert Norman}
\author[2]{Jamie Twycross}
\author[3]{John King}
\author[4]{Charlie Hodgman}
\author[1]{Nigel Minton}
\affil[1]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\affil[2]{Intelligent Modelling and Analysis group, School of Computer Science, University of Nottingham, Nottingham, NG8 1BB, United Kingdom}
\affil[3]{School of Mathematical Sciences, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\affil[4]{School of Biosciences, University of Nottingham, Sutton Bonington, Loughborough, LE12 5RD, United Kingdom}

\begin{document}

\maketitle

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{Testdriven.png}
\caption{Workflow for model development proposed for gsmodutils.
The objective of this approach is to simultaneously capture research questions, model validation criteria and minimise the impact of changes on previously completed models.
}
\label{fig:test_driven}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{inheritence.png}
  \label{fig:strain_hered}
  \caption{Examples of gsmodutils design inheritance.
  Each design stores the delta between the wild-type base model, any parents and the changes to constraints the design contains.
  In the example presented above a heterologous production pathway is combined with a reusable set of knock-outs.
  In practice, ideally, these designs should relate to real constructs and strains evaluated by wet lab biologists.
  }
\end{figure}

@@

\section*{Acknowledgements}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work and Thomas Millat for scientific advice.
This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) grants BB/L013940/1,  BB/K00283X/1 and BB/L502030/1.

\bibliographystyle{unsrt}
\bibliography{references}

\end{document}
\grid

>>>>

\author{James P Gilbert}
\email{james.gilbert@nottingham.ac.uk}
\author{Nicole Pearcy}
\author{Rupert Norman}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Jamie Twycross}
\affiliation[IMA]{Intelligent Modelling and Analysis group, School of Computer Science, University of Nottingham, Nottingham, NG8 1BB, United Kingdom}
\author{John King}
\affiliation[Maths]{School of Mathematical Sciences, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\author{Charlie Hodgman}
\affiliation[Biosciences]{School of Biosciences, University of Nottingham, Sutton Bonington, Loughborough, LE12 5RD, United Kingdom}
\author{Nigel Minton}
\affiliation[sbrc]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}

\title{Gsmodutils: A python based framework for test driven genome scale metabolic model development}

\begin{document}
\maketitle

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.8\textwidth]{testdriven.eps}
\caption{Workflow for model development proposed for gsmodutils.
The objective of this approach is to simultaneously capture research questions, model validation criteria and minimise the impact of changes on previously completed models.
}
\label{fig:test_driven}
\end{figure}

@@

\begin{figure}
  \includegraphics[width=\textwidth]{inheritence2.eps}
  \label{fig:strain_hered}
  \caption{Examples of gsmodutils design inheritance.
  Each design stores the delta between the wild-type base model, any parents and the changes to constraints the design contains.
  In the example presented above a heterologous production pathway is combined with a reusable set of knock-outs.
  In practice, ideally, these designs should relate to real constructs and strains evaluated by experiment.
  }
\end{figure}

@@

\begin{acknowledgement}
We would like to thank the Oxford Brookes Cell Systems Modelling group for helpful discussions regarding this work and Thomas Millat for scientific advice.
This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) grants BB/L013940/1,  BB/K00283X/1 and BB/L502030/1.
\end{acknowledgement}

\bibliographystyle{ieeetrans}
\bibliography{references}
\end{document}
